Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-03 paper/ms.tex
update paper

\begin{figure}[t]
	\begin{center}
		\leavevmode
    %\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
    \gridline{\fig{target_star_cumulative_counts.png}{0.45\textwidth}{}}
    \vspace{-0.8cm}
    \gridline{\fig{target_star_hist_logt.png}{0.45\textwidth}{}}
	\end{center}
	\vspace{-0.8cm}
	\caption{
    {\it Top.} Cumulative number of target stars as
    a function of Gaia $Rp$-band magnitude.  The selected stars are
    either candidate members of clusters, or else have other youth
    indicators (see \S~\ref{sec:starselection}). We only consider
    stars with $G_{\rm Rp} < 16$.
    {\it Bottom.} Histogram of target star ages, for the subset of
    stars with ages matched against \citet{Kharchenko_et_al_2013}.
	\label{fig:cdips_targets}
	}
\end{figure}

\begin{figure*}[!ht]
	\gridline{\fig{mwscmatchstats.png}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{dias14matchstats.png}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    {\it Top.} Cross-match statistics from
    \cite{Kharchenko_et_al_2013} cluster members to Gaia-DR2. A
    histogram of the distances between matched stars is on the left; a
    histogram of the difference between the true $G$-band magnitude
    and that predicted from 2MASS photometry is in the middle; a scatter
    plot of the same magnitude difference as a function of $G$-band
    magnitude is on the right.
    {\it Bottom.} Same, but cross-matching \cite{dias_proper_2014}
    cluster members to Gaia-DR2.
	}
	\label{fig:xmatch_info}
\end{figure*}

@@

\begin{figure}[!t]
	\gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
		Significance thresholds empirically defined for the transiting
		planet search described in \S~\ref{subsec:identifying_ctois}.
		Each point represents the TLS periodogram peak signal
		detection efficiency from one light curve.  {\it Top.} Sector
		6.  {\it Bottom.} Sector 7.
	}
	\label{fig:tlsresults}
\end{figure}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{quilt_PCs.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
		{\bf Phased light curves for six of the \numberpcs candidate
			transiting planets identified in this work.}
		Black points are detrended flux measurements, phased to the
		best-fit orbital period indicated in the lower right of each
		panel.
		Best-fit models are fit as described in \S~\ref{subsec:ctois}, and
		plotted with blue lines.
		For display purpses, a window of $\pm 4$ transit durations
		centered on the transit mid-point is displayed.
		The vetting reports for these objects are available at XXX.	%FIXME
		% TODO: include age? T mag?
		The Gaia source identifiers are
		a): 5605128927705695232, 
		b): 3125263468681400320, 
		c): 5510676828723793920, 
		d): 3007171311355035136, 
		e): 5617126180115568256, 
		f): 3220266049321724416.   
		\label{fig:ctoi_quilt}
	}
\end{figure*}

>>>>

\begin{figure}[t]
	\begin{center}
		\leavevmode
    %\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
    \gridline{\fig{target_star_cumulative_counts.png}{0.4\textwidth}{}}
    \vspace{-0.8cm}
    \gridline{\fig{target_star_hist_logt.png}{0.4\textwidth}{}}
    \vspace{-0.8cm}
    \gridline{\fig{target_star_reference_pie_chart.png}{0.4\textwidth}{}}
	\end{center}
	\vspace{-0.8cm}
	\caption{
    {\it Top.} Cumulative counts of target stars as
    a function of Gaia $Rp$-band magnitude.  The stars are
    either candidate members of clusters, or else have other youth
    indicators (see \S~\ref{sec:starselection}). We only consider
    stars with $G_{\rm Rp} < 16$.
    {\it Middle.} Histogram of target star ages, for the subset of
    stars with ages matched against \citet{Kharchenko_et_al_2013}.
    {\it Bottom.} Provenance of cluster membership.  Percentages are
    relative to $N_{\rm total}=1061446$ target stars. Symbols
    are as follows.
    D14 is \citet{dias_proper_2014}.
    K13 is \citet{Kharchenko_et_al_2013}.
    CG18 is \citet{cantat-gaudin_gaia_2018}.
    Z18 is \citet{zari_3d_2018}, with upper main sequence and
    pre-main-sequence samples sub-divided.
    ``$\geq 2$'' indicates at least two authors reported a star as a
    candidate cluster member.
    %``Other'' refers to sources enumerated in \S~\ref{sec:starselection}.
	\label{fig:cdips_targets}
	}
\end{figure}

\begin{figure*}[!ht]
	\gridline{\fig{mwscmatchstats.png}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{dias14matchstats.png}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    {\it Top.} Quality diagnostics from cross-matching
    \cite{Kharchenko_et_al_2013} cluster members against Gaia-DR2.
    histogram of the distances between matched stars is on the left; a
    histogram of the difference between the true $G$-band magnitude
    and that predicted from 2MASS photometry is in the middle; a scatter
    plot of the same magnitude difference as a function of $G$-band
    magnitude is on the right.
    {\it Bottom.} Same, but cross-matching \cite{dias_proper_2014}
    cluster members to Gaia-DR2.
	}
	\label{fig:xmatch_info}
\end{figure*}

@@

\begin{figure}[!t]
	\gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    (IN PROGRESS) Significance thresholds empirically defined for the
    transiting planet search described in
    \S~\ref{subsec:identifying_ctois}.  Each point represents the TLS
    periodogram peak signal detection efficiency from one light curve.
    {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
	}
	\label{fig:tlsresults}
\end{figure}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{quilt_PCs.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
		{\bf Phased light curves for six of the \numberpcs candidate
			transiting planets identified in this work.}
		Black points are detrended flux measurements, phased to the
		best-fit orbital period indicated in the lower right of each
		panel.
    Transit models are fitted as described in \S~\ref{subsec:ctois},
    and plotted with blue lines.
		For display purposes, a window of $\pm 4$ transit durations
		centered on the transit mid-point is displayed.
		The vetting reports for these objects are available at XXX.	%FIXME
		% TODO: include age? T mag?
		The Gaia source identifiers are
		a): 5605128927705695232, 
		b): 3125263468681400320, 
		c): 5510676828723793920, 
		d): 3007171311355035136, 
		e): 5617126180115568256, 
		f): 3220266049321724416.   
		\label{fig:ctoi_quilt}
	}
\end{figure*}
